---
title: "create_summary_table"
author: 
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Tranmitter Summary

* id_ptt = transmitter ID (IDs beginning 197 are adults, 229 are juveniles)
* date_recent = timestamp on the most recent message from the transmitter
* recent_temp = temperature of the transmitter from the most recent message in degrees Celsius
* mean_temp = average temperature of transmitter from the 5 most recent messages in degrees Celsius
* volts_mean = average transmitter battery voltage over 5 most recent messages
* status: 
  + active = transmitter is warm and providing locations at or near the expected frequency
  + ambiguous = transmitter was last detected warm, but is no longer providing locations
  + messages_only = transmitter is warm and providing messages, but without sufficient data to determine its location
  + cold = transmitter detected cold, indicating a mortality
        

```{r load packages, message = FALSE}
# got packages?
library(workflowr)# git version tracking to repository
library(move) # functions to access data from Movebank
library(knitr)
```

```{r create table, warning = FALSE, message = FALSE}
# set current date
today <- Sys.Date()

# source Movebank login info to protect password
source("code/login_movebank_rizzolo.R")

# get Movebank project info
FwsName <- "Spectacled_Eider_USFWS_Alaska"
studyIdFws <- getMovebankID(FwsName, login=Login)

# download location data
locs_fws <- getMovebankLocationData(study=FwsName, sensorID="Argos Doppler Shift", login=Login, includeOutliers=TRUE)
# warning messages from old residual reference data that Movebank is not deleting with each new ref data upload, for some reason
# does not effect the current data

### download reference data into a data frame....
ref_fws <- getMovebankReferenceTable(study=FwsName,login=Login)

# retain unchanged dataframe
#arch_locs <- locs_fws
locs <- locs_fws

# format date and subset transmitters with timestamp year > 2021
locs$timestamp <- as.POSIXct(locs$timestamp, format="%Y-%m-%d %H:%M:%S", tz = 'UTC')
thisyear <- subset(locs, format(locs$timestamp, format("%Y")) > 2021)

# select most recent record for each transmitter ID
recent<-thisyear[
  tapply(1:nrow(thisyear), thisyear$tag.local.identifier, function(ii) ii[which.max(thisyear$timestamp[ii])])
  ,]

# 1. Get date and sensor 1 (ptt temp) data from most the recent location for each transmitter ID ####
# create dateframe with most recent date for each transmitter ID
date_recent <- cbind.data.frame(id_ptt = recent$tag.local.identifier, date_recent = recent$timestamp)

# number of days since last location
date_recent$days_since_last_loc <- as.numeric(today-as.Date(date_recent$date_recent))
date_recent$days_since_last_loc <- ifelse(date_recent$days_since_last_loc < 1, 0, date_recent$days_since_last_loc)

# number of missed duty cycles, where adult PTTs (IDs 197###) is every 7 d, and juveniles (221###) is every 2 d
date_recent$missed_cycles <- ifelse(date_recent$id_ptt < 229000, date_recent$days_since_last_loc/7, date_recent$days_since_last_loc/2)
date_recent$missed_cycles <- round(date_recent$missed_cycles,1)
date_recent$missed_cycles <- ifelse(date_recent$missed_cycles < 1, 0, date_recent$missed_cycles)

# create object with most recent sensor1 data from each PTT
recent_temp <- cbind.data.frame(id_ptt = recent$tag.local.identifier, recent_temp = recent$argos.sensor.1)

# transform sensor1 data to deg C
recent_temp$recent_temp <- -28.68 + 0.3609*recent$argos.sensor.1

# 2. Get mean transmitter temperature and voltage from 5 most recent records for each transmitter ID ####
# remove records with argos.sensor.1 data not related to temperature by first...
# removing NA data for transmitter sensor 1 (temperature) indicated with -999
locs_temp <- subset(thisyear,  argos.sensor.1 != -999) # and then,

# removing special transmission data (every 4th duty cycle) indicated by  argos.sensor.3 = 0 (see MTI Battery Powered PTT-100 Field Manual, p 17)
locs_temp <- subset(locs_temp,  argos.sensor.3 != 0)

# Get most recent data for each transmitter by
# sub-setting 5 most recent records by timestamp for each ID
# first, order by timestamp for each ID
locs_temp <- locs_temp[order(locs_temp$timestamp, decreasing = TRUE), ]

# then, subset to 5 most recent records per ID
five <- Reduce(rbind, by(locs_temp,
                       locs_temp["tag.local.identifier"],
                       head,
                       n = 5))

# calculate mean transmitter values over 5 most recent obs by transmitter
mean_temp <- aggregate(argos.sensor.1 ~ five$tag.local.identifier, data = five, FUN="mean")

# convert sensor.1 values to deg C (from Microwave Telem field manual)
mean_temp$mean_temp <- -28.68 + 0.3609*mean_temp$argos.sensor.1

colnames(mean_temp) <- c("id_ptt", "sensor1", "mean_temp")
mean_temp <- mean_temp[, -2] # remove unneeded untransformed value column

# get body temp ready from the most recently received PTT message

# calculate mean transmitter voltage over 5 most recent obs by transmitter
volts_mean <- aggregate(argos.sensor.2 ~ five$tag.local.identifier, data = five, FUN="mean")

# convert sensor 2 values to volts  (from Microwave Telem field manual)
volts_mean$volts_mean <- 2.978 + 0.0041*volts_mean$argos.sensor.2

colnames(volts_mean) <- c("id_ptt", "sensor2", "volts_mean")
volts_mean <- volts_mean[, -2] # remove unneeded untransformed value column

# merge recent date and temperature by transmitter ID
ptt_sum <- merge(date_recent[, -3], recent_temp, by = "id_ptt")
ptt_sum <- merge(ptt_sum, mean_temp, by = "id_ptt")
ptt_sum <- merge(ptt_sum, volts_mean, by ="id_ptt")

# create dataframe of transmitter fates
id_ptt_ad <- seq(197559, 197598,1)
id_ptt_juv <- c("229950","229951","229952", "229953","229954","229955","229957","229958","229961","229963","229964","229965")
id_ptt_juv <- as.numeric(id_ptt_juv)
id_ptt <- c(id_ptt_ad, id_ptt_juv)

# from tbl_fates in database spei_ptt_2018_2022.accdb
status <- c("active", #197559
            "active", #197560
            "active", #197561
            "active", #197562
            "cold", #197563
            "active", #197564
            "active", #197565
            "active", #197566
            "active", #197567
            "active",#197568
           "ambiguous", #197569
           "active",#197570
           "ambiguous",#197571
           "active",#197572
           "ambiguous",#197573
           "active",#197574
           "active", #197575
           "ambiguous", #197576
           "active", #197577
           "active", #197578
           "active", #197579
           "active",#197580
           "cold", #197581 
           "active", #197582
           "active", #197583
           "cold", #197584
           "active", #197585
           "active", #197586
           "cold", #197587
           "cold", #197588
           "active", #197589
           "active", #197590
           "active", #197591
           "ambiguous", #197592
           "active", #197593
           "active", #197594
           "active", #197595
           "active", #197596
           "active", #197597
           "active", #197598
           "ambiguous", #229950
           "ambiguous", #229951
           "cold", #229952
           "cold",#229953
           "cold",#229954
           "active", #229955
           "cold", #229957
           "active",#229958
           "active", #229961
           "cold", #229963
           "cold", #229964
           "cold") #229965

fates_df <- data.frame(id_ptt, status)

ptt_sum <- merge(ptt_sum, fates_df, by = "id_ptt")

# sort
ptt_sum <- ptt_sum[order(ptt_sum$date_recent, decreasing = TRUE), ]

# how many PTTs in table (should be 52 that were deployed in 2022)
ptt_count <- nrow(ptt_sum)

#print(ptt_sum)
# missing PTTs (should be n = 52):
# 197563: Dead. First cold on 06 June 2022. Last warm on 18 May 2022.
# 197566: transmitter message with no location (too few messages) on 02 Nov 2022, at which time PTT was warm. Last message with location was 12 June 2022.
#         Poor transmitter performance.

kable(ptt_sum[ ,-3], row.names = FALSE)
```

```{r status summary, message = FALSE}
table(fates_df$status)
```
