---
title: "Recent SPEI Transmitter Locations"
author:
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# NB Curl not downloading geotifs correctly as of 20231120, commented out download code with ###***
# changed to using the httr package and httr function in March 2024
# got packages?
library(leaflet) # interactive map
library(tidyverse) # whatever
library(move)   # must be move version 3.3.0+; to access Movebank data
library(htmltools) # apply html syntax used in leaflet map
library(raster) # working with ice geotif
library(sp) # for re-projecting raster
library(sf) # reading in KML of survey area
library(httr) # to download geotifs from Univ Bremen, download.file function stopped working in late 2023 for some unknown reason

# set current date
today<-Sys.Date()
yesterday <- Sys.Date()-1
```

Locations were downloaded from the Movebank.org data repository on `r today`.
```{r login download data, warning = FALSE}
# load most recent data from Movebank
#Login<-movebankLogin(username = username, password = password)
# use sourced script to login
source("code/login_movebank_rizzolo.R", local = knitr::knit_global())

# get Movebank project info
FwsName <- "Spectacled_Eider_USFWS_Alaska"
studyIdFws <- getMovebankID(FwsName, login=Login)

### Read the Movebank location data into a data frame
locs_fws <- getMovebankLocationData(study=FwsName, sensorID="Argos Doppler Shift", login=Login, includeOutliers=TRUE)
# warning messages from old residual reference data that Movebank is not deleting with each new ref data upload, for some reason
# does not effect the current data

### Read the associated Movebank reference data into a data frame.
ref_fws <- getMovebankReferenceTable(study=FwsName,login=Login)

```

Data were not filtered before plotting. All locations received during each duty cycle were included. Two weeks of data prior to the date the data were downloaded are shown.
```{r data filtering, warning = FALSE}
# combine locations and reference data for filtered locations
#alldata <- dplyr::left_join(locs_fws, ref_fws,
#                                 by=c("deployment.id" = "deployment_id",
#                                      "sensor.type.id" = "sensor_type_id"))
#alldata <- dplyr::left_join(locs_fws, ref_fws,
#                                 by=c("tag.local.identifier" = "tag_local_identifier"))

# get tag id to match between ref and locs data frames for merge
names(ref_fws)[names(ref_fws) == "tag_local_identifier"] <- "tag.local.identifier"
# merge all locs to matching ref by tag id
alldata <- merge(locs_fws, ref_fws, by = "tag.local.identifier", all.x = TRUE)
# convert sensor 1 PTT temp from untransformed value to degrees F (PTT temps will be displayed in map)
alldata$tempC <- round(-28.682 + 0.3609 * alldata$argos.sensor.1, 1)
#alldata$tempF <- (alldata$tempC * 1.8) + 32

# remove location classes with no measurement of precision
keep <- c("3", "2", "1", "0")
locs_lc <- alldata[alldata$argos.lc %in% keep,]

##### filter locations from transmitters colder than 25 C ####
locs_lc$tempKeep <- ifelse(locs_lc$tempC < 25, 0, 1)
locs_lc <- subset(locs_lc, tempKeep == 1)

# select locations from most recent 2 weeks
fourweeks <- subset(locs_lc, timestamp > today-28)

twoweeks <- subset(fourweeks, timestamp > today-14)

fourdays <- subset(twoweeks, timestamp > today-4)

twodays <- subset(twoweeks, timestamp > today-2)

# save locations
filename <- paste('spei_ptt_four_weeks_', today, sep = "")
filename <- paste(filename, ".csv", sep = "")
write.csv(fourweeks, paste('output/', filename, sep = ""))

# remove locations marked as outliers based on movement rates and directions using Douglas Argos Filter, which is run in Movebank
#table(locs_fws$algorithm.marked.outlier)
locs_filter <- subset(fourweeks, algorithm.marked.outlier != "true")

# create data frame of locations marked by DAF as likely outliers to plot along with filtered locations
improb <- subset(fourweeks, algorithm.marked.outlier == "true")

# define range of data and sample size for locations and transmitters
min_date <- min(fourweeks$timestamp)
max_date <- max(fourweeks$timestamp)
ptts <- unique(fourweeks$tag.local.identifier)
ptt_count <- length(ptts)
location_count <-length(fourweeks)

ptts2wk <- unique(twoweeks$tag.local.identifier)
ptt2wk_count <- length(ptts2wk)
location_count2wk <-length(twoweeks)

ptts4d <- unique(fourdays$tag.local.identifier)
ptt4d_count <- length(ptts4d)
location_count4d <-length(fourdays)

ptts2d <- unique(twodays$tag.local.identifier)
ptt2d_count <- length(ptts2d)
location_count2d <-length(twodays)

```


```{r data seaice, warning = FALSE, , include=FALSE}
# R code to download sea ice concentration data from the University of Bremen
# data format = geotif, *.tif, at 6.25 km pixel size
# Bremen sea ice concentration data: https://seaice.uni-bremen.de/databrowser/#p=sic
# Set date for download
# Daily data are available today -1 day
date <- format(yesterday, "%Y%m%d")
Month <- format(yesterday, "%b")
month <- tolower(Month)

# Create Bremen URL: https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n3125/2024/jan/[REGION]/asi-AMSR2-n3125-[DATE]-v5.4.tif
# Arctic-wide raster with 6.25 km pixel size
URL_arctic_start <- "https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n6250/2025/"
URL_artic_month <- paste(URL_arctic_start, month, sep="")
URL_arctic_region <- paste(URL_artic_month, "/Arctic/", sep = "")
filename_arctic_start <- paste("asi-AMSR2-n6250-", date, sep = "")
filename_arctic <- paste(filename_arctic_start, "-v5.4.tif", sep="")
url_arctic <- paste(URL_arctic_region, filename_arctic, sep="")

# Specify download destination
destfile <- paste("source/bremen_sic_tif/", filename_arctic, sep = "")
httr::GET(url_arctic, httr::write_disk(path=destfile, overwrite = TRUE))

# Format it
ice_arctic <- raster(paste('source/bremen_sic_tif/', filename_arctic, sep = ""))

# Check CRS
#crs.ice_arctic <- projection(ice_arctic)

# reproject to lat lon WGS84
raster::projectExtent(ice_arctic, crs = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
#projection(ice_arctic)

# repeat for Bering Strait raster at smaller pixel size, 3.125 km
URL_bs_start <- "https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n3125/2025/"
URL_bs_month <- paste(URL_bs_start, month, sep="")
URL_bs_region <- paste(URL_bs_month, "/Beringstrait/", sep = "")
filename_bs_start <- paste("asi-AMSR2-n3125-", date, sep = "")
filename_bs <- paste(filename_bs_start, "-v5.4.tif", sep= "")
url_bs <- paste(URL_bs_region, filename_bs, sep= "")
destfile2 <- paste("source/bremen_sic_tif/", filename_bs, sep = "")
###***download.file(url = url_bs, destfile = destfile, method = 'curl') #stopped working, replaced with httr in March 2024
httr::GET(url_bs, httr::write_disk(path=destfile2, overwrite = TRUE))
ice_bs <- raster(paste('source/bremen_sic_tif/', filename_bs, sep = ""))
raster::projectExtent(ice_bs, crs = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

# Check CRS
#crs.ice_bs <- projection(ice_bs)

# merge Artic with BS rasters
#ice <- raster::merge(ice_arctic, ice_bs)
#ice <- ice_bs

# add survey area
survey <- st_read("data/gis/optional.polygon.kml")
```
The oldest transmitter location timestamp in this map is `r min_date`.

The most recent transmitter location timestamp in this map is `r max_date`.

`r location_count` locations from `r ptt_count` transmitters are shown in this map

Sea ice concentration data from University of Bremen are from `r yesterday`.
Arctic sea ice concentration pixel size is 6.25 km.
Bering sea ice concentration pixe size is 3.12 km.

Hover the cursor over a point to show information related to that location.

Select the background map from menu in upper-right corner (sea ice concentration in the Arctic at 6.25 km resolution, sea ice concentration in the Bering Strait at 3.12 km resolution, or satellite image).

Select the most recent 2 weeks of locations (red points) or most recent 2 days (1 duty cycle) of locations (yellow points) in the upper right corner.

Data on sea ice concentration from the University of Bremen are available [here](https://seaice.uni-bremen.de/data/amsr2/today/Beringstrait_AMSR2_visual.png).

Information on remotely sensed sea ice data is [here](https://seaice.uni-bremen.de/fileadmin/user_upload/ASIuserguide.pdf)

```{r leaflet map, warning = FALSE}
# ice palette
pal_arctic <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values (ice_arctic), na.color = "#FFFFCC")
pal_bs <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values (ice_bs), na.color = "#FFFFCC")

# map 'em
m <- leaflet() %>%
  setView(lng = -170, lat = 63.5, zoom = 4) %>%
  # add base layers
  # Sea ice Concentration
  addRasterImage(ice_arctic, colors = pal_arctic, opacity = 0.8, group = "Arctic_sea_ice") %>%
  addRasterImage(ice_bs, colors = pal_bs, opacity = 0.8, group = "Bering_sea_ice") %>%
#  addLegend(pal = pal_arctic, values = values((ice_bs/250)*100),
#    title = "% Sea Ice Concentration") %>%
  # Satellite Imagery
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>%
  addScaleBar(position = 'topright') %>%
  # add overlay groups
  # most recent 4 weeks of data
  addCircles(data = fourweeks,
             ~ location.long,
             ~ location.lat,
             color = "red",
             group ="FourWeeks",
             label = paste("ID:", fourweeks$individual.local.identifier, "<br>",
                           "Loc Date:", fourweeks$timestamp, "<br>",
                           "Deploy Site:", fourweeks$study_site, "<br>",
                           "Sex:", ifelse(fourweeks$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(fourweeks$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(fourweeks$argos.sensor.3 != 0, fourweeks$tempC, "NA"), "<br>",
                           "Location class", fourweeks$argos.lc) %>%          
               lapply(htmltools::HTML)) %>%
  # most recent 2 weeks
  addCircles(data = twoweeks,
             ~ location.long,
             ~ location.lat,
             color = "orange",
             group ="TwoWeeks",
             label = paste("ID:", twoweeks$individual.local.identifier, "<br>",
                           "Loc Date:", twoweeks$timestamp, "<br>",
                           "Deploy Site:", twoweeks$study_site, "<br>",
                           "Sex:", ifelse(twoweeks$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(twoweeks$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(twoweeks$argos.sensor.3 != 0, twoweeks$tempC, "NA"), "<br>",
                           "Location class", twoweeks$argos.lc) %>%          
               lapply(htmltools::HTML)) %>%
  # most recent 2 days of data (1 duty cycle)
  addCircles(data = twodays,
             ~ location.long,
             ~ location.lat,
             color = "yellow",
             group ="TwoDays",
             label = paste("ID:", twodays$individual.local.identifier, "<br>",
                           "Loc Date:", twodays$timestamp, "<br>",
                           "Deploy Site:", twodays$study_site, "<br>",
                           "Sex:", ifelse(twodays$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(twodays$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(twodays$argos.sensor.3 != 0, twodays$tempC, "NA"), "<br>",
                           "Location class", twodays$argos.lc) %>%          
               lapply(htmltools::HTML))%>%
    # add layer controls
  addLayersControl(
     baseGroups = c("Satellite", "Arctic_sea_ice", "Bering_sea_ice"),
#      baseGroups = c("Satellite", "Sea Ice: Arctic 6.25 km pixel"),
      overlayGroups = c("FourWeeks", "TwoWeeks", "TwoDays"),
      options = layersControlOptions(collapsed = FALSE),
      position = 'topright'
    ) %>%
  # add measurement
  addMeasure(
    primaryLengthUnit = "kilometers",
    secondaryLengthUnit = 'miles',
    primaryAreaUnit = "sqmeters",
    secondaryAreaUnit = "acres",
    position = 'topleft'
  )

#m <- m %>%
#  addPolygons(
#    data = survey
#  )
m

```
