---
title: "Recent SPEI Transmitter Locations"
author: 
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# got packages?
library(leaflet) # interactive map
library(tidyverse) # whatever
library(move)   # must be move version 3.3.0+; to access Movebank data
library(htmltools) # apply html syntax used in leaflet map
library(raster) # working with ice geotif
library(sp) # for re-projecting raster 

# set current date
today<-Sys.Date()
yesterday <- Sys.Date()-1
```

Locations were downloaded from the Movebank.org data repository on `r today`.
```{r login download data, warning = FALSE}
# load most recent data from Movebank
#Login<-movebankLogin(username = username, password = password) 
# use sourced script to login
source("code/login_movebank_rizzolo.R", local = knitr::knit_global())

# get Movebank project info
FwsName <- "Spectacled_Eider_USFWS_Alaska"
studyIdFws <- getMovebankID(FwsName, login=Login)

### Read the Movebank location data into a data frame
locs_fws <- getMovebankLocationData(study=FwsName, sensorID="Argos Doppler Shift", login=Login, includeOutliers=TRUE)
# warning messages from old residual reference data that Movebank is not deleting with each new ref data upload, for some reason
# does not effect the current data

### Read the associated Movebank reference data into a data frame.
ref_fws <- getMovebankReferenceTable(study=FwsName,login=Login)

```

Data were not filtered before plotting. All locations received during each duty cycle were included. Two weeks of data prior to the date the data were downloaded are shown.
```{r data filtering, warning = FALSE}
# combine locations and reference data for filtered locations
alldata <- dplyr::left_join(locs_fws, ref_fws,
                                 by=c("deployment.id" = "deployment_id", "sensor.type.id" = "sensor_type_id"))
# convert sensor 1 PTT temp from untransformed value to degrees F (PTT temps will be displayed in map)
alldata$tempC <- round(-28.682 + 0.3609 * alldata$argos.sensor.1, 1)
#alldata$tempF <- (alldata$tempC * 1.8) + 32

# select locations from most recent 2 weeks
fourweeks <- subset(alldata, timestamp > today-28)

twoweeks <- subset(fourweeks, timestamp > today-14)

twodays <- subset(twoweeks, timestamp > today-2)

# save locations
filename <- paste('spei_ptt_four_weeks_', today, sep = "")
filename <- paste(filename, ".csv", sep = "")
write.csv(fourweeks, paste('output/', filename, sep = ""))

# remove locations marked as outliers based on movement rates and directions using Douglas Argos Filter, which is run in Movebank
#table(locs_fws$algorithm.marked.outlier)
locs_filter <- subset(fourweeks, algorithm.marked.outlier != "true")

# create data frame of locations marked by DAF as likely outliers to plot along with filtered locations
improb <- subset(fourweeks, algorithm.marked.outlier == "true")

# define range of data and sample size for locations and transmitters
min_date <- min(fourweeks$timestamp)
max_date <- max(fourweeks$timestamp)
ptts <- unique(fourweeks$tag_local_identifier)
ptt_count <- length(ptts)
location_count <-length(fourweeks) 
```


```{r data seaice, include=FALSE, warning = FALSE}
# R code to download sea ice concentration data from the University of Bremen
# data format = geotif, *.tif, at 6.25 km pixel size
# Bremen sea ice concentration data: https://seaice.uni-bremen.de/databrowser/#p=sic
# Set date for download 
# Daily data are available today -1 day
date <- format(yesterday, "%Y%m%d")
Month <- format(yesterday, "%b")
month <- tolower(Month)

# Create Bremen URL: https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n3125/2023/jan/[REGION]/asi-AMSR2-n3125-[DATE]-v5.4.tif
# Arctic-wide raster
#URL_arctic_start <- "https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n6250/2023/" 
#URL_artic_month <- paste(URL_arctic_start, month, sep="")
#URL_arctic_region <- paste(URL_artic_month, "/Arctic/", sep = "")
#filename_arctic_start <- paste("asi-AMSR2-n6250-", date, sep = "")
#filename_arctic <- paste(filename_arctic_start, "-v5.4.tif", sep="")
#url_arctic <- paste(URL_arctic_region, filename_arctic, sep="")

# Specify download destination 
#destfile <- paste("source/bremen_sic_tif/", filename_arctic, sep = "")

# Download it
#download.file(url = url_arctic, destfile = destfile, method = 'curl')

# Format it
#ice_arctic <- raster(paste('source/bremen_sic_tif/', filename_arctic, sep = ""))

# Check CRS
#crs.ice <- projection(ice)

# reproject to lat lon WGS84
#raster::projectExtent(ice_arctic, crs = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
#projection(ice)

# repeat for Bering Strait raster at smaller pixel size
URL_bs_start <- "https://seaice.uni-bremen.de/data/amsr2/asi_daygrid_swath/n3125/2023/" 
URL_bs_month <- paste(URL_bs_start, month, sep="")
URL_bs_region <- paste(URL_bs_month, "/Beringstrait/", sep = "")
filename_bs_start <- paste("asi-AMSR2-n3125-", date, sep = "")
filename_bs <- paste(filename_bs_start, "-v5.4.tif", sep= "")
url_bs <- paste(URL_bs_region, filename_bs, sep= "")
destfile <- paste("source/bremen_sic_tif/", filename_bs, sep = "")
download.file(url = url_bs, destfile = destfile, method = 'curl')
ice_bs <- raster(paste('source/bremen_sic_tif/', filename_bs, sep = ""))
raster::projectExtent(ice_bs, crs = sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

# merge Artic with BS rasters
#ice <- raster::merge(ice_arctic, ice_bs)
ice <- ice_bs
```
The oldest transmitter location timestamp in this map is `r min_date`.

The most recent transmitter location timestamp in this map is `r max_date`.

`r location_count` locations from `r ptt_count` transmitters are shown in this map

Sea ice concentration data from University of Bremen are from `r yesterday`.

Hover the cursor over a point to show information related to that location. 

Select the background map from menu in upper-right corner (sea ice concentration or satellite image).

Select the most recent 2 weeks of locations (red points) or most recent 2 days (1 duty cycle) of locations (yellow points) in the upper right corner.

Data on sea ice concentration from the University of Bremen are available [here](https://seaice.uni-bremen.de/data/amsr2/today/Beringstrait_AMSR2_visual.png).

Information on remotely sensed sea ice data is [here](https://seaice.uni-bremen.de/fileadmin/user_upload/ASIuserguide.pdf)

```{r leaflet map, warning = FALSE}
# ice palette
pal <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values (ice), na.color = "#FFFFCC")

# map 'em
m <- leaflet() %>%
  setView(lng = -170, lat = 63.5, zoom = 6) %>%
  # add base layers
  # Sea ice Concentration
  addRasterImage(ice, colors = pal, opacity = 0.8) %>% 
  addLegend(pal = pal, values = values((ice/250)*100),
    title = "% Sea Ice Concentration") %>% 
  # Satellite Imagery
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>%
  addScaleBar(position = 'topright') %>%
  # add overlay groups
  # most recent 4 weeks of data
  addCircles(data = fourweeks,
             ~ location.long,
             ~ location.lat,
             color = "red",
             group ="FourWeeks",
             label = paste("ID:", improb$individual.local.identifier, "<br>",
                           "Loc Date:", improb$timestamp, "<br>",
                           "Deploy Site:", improb$study_site, "<br>",
                           "Sex:", ifelse(improb$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(improb$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(locs_filter$argos.sensor.3 != 0, locs_filter$tempC, "NA"), "<br>",
                           "Location class", locs_filter$argos.lc) %>%           
               lapply(htmltools::HTML)) %>% 
  # most recent 2 weeks
  addCircles(data = twoweeks,
             ~ location.long,
             ~ location.lat,
             color = "orange",
             group ="TwoWeeks",
             label = paste("ID:", improb$individual.local.identifier, "<br>",
                           "Loc Date:", improb$timestamp, "<br>",
                           "Deploy Site:", improb$study_site, "<br>",
                           "Sex:", ifelse(improb$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(improb$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(locs_filter$argos.sensor.3 != 0, locs_filter$tempC, "NA"), "<br>",
                           "Location class", locs_filter$argos.lc) %>%           
               lapply(htmltools::HTML)) %>% 
  # most recent 2 days of data (1 duty cycle)
  addCircles(data = twodays,
             ~ location.long,
             ~ location.lat,
             color = "yellow",
             group ="TwoDays",
             label = paste("ID:", improb$individual.local.identifier, "<br>",
                           "Loc Date:", improb$timestamp, "<br>",
                           "Deploy Site:", improb$study_site, "<br>",
                           "Sex:", ifelse(improb$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(improb$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(locs_filter$argos.sensor.3 != 0, locs_filter$tempC, "NA"), "<br>",
                           "Location class", locs_filter$argos.lc) %>%           
               lapply(htmltools::HTML))%>% 
    # add layer controls
  addLayersControl( 
      baseGroups = c("Satellite", "Sea Ice Concentration"),
      overlayGroups = c("FourWeeks", "TwoWeeks", "TwoDays"),
      options = layersControlOptions(collapsed = FALSE),
      position = 'topright'
    ) %>% 
  # add measurement
  addMeasure(
    primaryLengthUnit = "kilometers",
    secondaryLengthUnit = 'miles',
    primaryAreaUnit = "sqmeters",
    secondaryAreaUnit = "acres",
    position = 'topleft'
  )
m

```

