---
title: "Map"
author: 
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# got packages?
library(leaflet) # interactive map
library(tidyverse) # whatever
library(move)   # must be move version 3.3.0+; to access Movebank data
library(htmltools) # apply html syntax used in leaflet map

# set current date
today<-Sys.Date()
```

Locations were downloaded from the Movebank.org data repository on `r today`.
```{r login download data, warning = FALSE}
# load most recent data from Movebank
#Login<-movebankLogin(username = username, password = password) 
# use sourced script to login
source("code/login_movebank_rizzolo.R", local = knitr::knit_global())

# get Movebank project info
FwsName <- "Spectacled_Eider_USFWS_Alaska"
studyIdFws <- getMovebankID(FwsName, login=Login)

### Read the Movebank location data into a data frame
locs_fws <- getMovebankLocationData(study=FwsName, sensorID="Argos Doppler Shift", login=Login, includeOutliers=TRUE)
# warning messages from old residual reference data that Movebank is not deleting with each new ref data upload, for some reason
# does not effect the current data

### Read the associated Movebank reference data into a data frame.
ref_fws <- getMovebankReferenceTable(study=FwsName,login=Login)

```

Data were not filtered before plotting. All locations received during each duty cycle were included. Two weeks of data prior to the date the data were downloaded are shown.
```{r data filtering, warning = FALSE}
# combine locations and reference data for filtered locations
alldata <- dplyr::left_join(locs_fws, ref_fws,
                                 by=c("deployment.id" = "deployment_id", "sensor.type.id" = "sensor_type_id"))
# convert sensor 1 PTT temp from untransformed value to degrees F (PTT temps will be displayed in map)
alldata$tempC <- round(-28.682 + 0.3609 * alldata$argos.sensor.1, 1)
#alldata$tempF <- (alldata$tempC * 1.8) + 32

# select locations from most recent 2 weeks
recent <- subset(alldata, timestamp > today-14)

# save locations
filename <- paste('spei_ptt_two_weeks_', today, sep = "")
filename <- paste(filename, ".csv", sep = "")
write.csv(recent, paste('output/', filename, sep = ""))

# remove locations marked as outliers based on movement rates and directions using Douglas Argos Filter, which is run in Movebank
#table(locs_fws$algorithm.marked.outlier)
locs_filter <- subset(recent, algorithm.marked.outlier != "true")

# create data frame of locations marked by DAF as likely outliers to plot along with filtered locations
improb <- subset(recent, algorithm.marked.outlier == "true")

# define range of data and sample size for locations and transmitters
min_date <- min(recent$timestamp)
max_date <- max(recent$timestamp)
ptts <- unique(recent$tag_local_identifier)
ptt_count <- length(ptts)
location_count <-length(recent) 
```

The oldest transmitter location timestamp in this map is `r min_date`.

The most recent transmitter location timestamp in this map is `r max_date`.

`r location_count` locations from `r ptt_count` transmitters are shown in this plot.

Hover the cursor over a point to show information related to that location. 

Select the background map from menu in upper-right corner (bathymetric, or satellite image).

Current data on sea ice concentration from the University of Bremen are available [here](https://seaice.uni-bremen.de/data/amsr2/today/Beringstrait_AMSR2_visual.png).

```{r leaflet map, warning = FALSE}
# map 'em
m <- leaflet() %>%
  setView(lng = -170, lat = 63.5, zoom = 6) %>%
  addProviderTiles("Esri.OceanBasemap", group = "Ocean Basemap") %>%
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>%
  addLayersControl( baseGroups = c("Ocean Basemap",
                  "Satellite"),
    options = layersControlOptions(collapsed = FALSE),
    position = 'topright'
  ) %>% 
  addScaleBar(position = 'topright') %>%
  addMeasure(
    primaryLengthUnit = "kilometers",
    secondaryLengthUnit = 'miles',
    primaryAreaUnit = "sqmeters",
    secondaryAreaUnit = "acres",
    position = 'topleft'
  ) %>%
  addCircles(data = improb,
             ~ location.long,
             ~ location.lat,
             color = "red",
             label = paste("ID:", improb$individual.local.identifier, "<br>",
                           "Loc Date:", improb$timestamp, "<br>",
                           "Deploy Site:", improb$study_site, "<br>",
                           "Sex:", ifelse(improb$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(improb$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(locs_filter$argos.sensor.3 != 0, locs_filter$tempC, "NA"), "<br>",
                           "Location class", locs_filter$argos.lc) %>%           
               lapply(htmltools::HTML)
)%>%
addCircles(data = locs_filter,
             ~ location.long,
            ~ location.lat,
             color = "red",
             label = paste("ID:", locs_filter$individual.local.identifier, "<br>",
                           "Loc Date:", locs_filter$timestamp, "<br>",
                           "Deploy Site:", locs_filter$study_site, "<br>",
                           "Sex:", ifelse(locs_filter$animal_sex == "f", "Female", "Male"), "<br>",
                           "Age:", ifelse(locs_filter$tag.local.identifier > 198000, "Juv", "Adult"), "<br>",
                           "PTT temp (alive is ~ 40 C):", ifelse(locs_filter$argos.sensor.3 != 0, locs_filter$tempC, "NA"), "<br>",
                           "Location class", locs_filter$argos.lc) %>%
               lapply(htmltools::HTML)
 )
m

```

