---
title: "Transmitter temperatures"
author: 
date: "`r Sys.Date()`"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# got packages?
library(ggplot2) # plot data
library(gridExtra) # create PDF plots
library(move) # to access data in Movebank

# set current date
today<-Sys.Date()
yesterday <- as.POSIXct(today-1)
```

Data transmitted by each active satellite transmitter includes the temperature of the transmitter (sensor 1 data). Transmitter temperature is the body temperature of the eider and should be ~ 40 째C. Transmitters in dead birds will be ambient temperature. 

This code downloads data from satellite transmitters deployed by the USFWS from Movebank.org, which is setup with a live feed of data from all active transmitters and is a repository for all data from transmitters that are no longer active.

As eiders are detected consistently cold, indicating a mortality, I define the deployment end date from that transmitter in Movebank so that locations from the cold transmitter are not shown beyond the date of the mortality. 

```{r loginto  Movebank}
# load most recent data from Movebank
#Login<-movebankLogin(username = username, password = password) 
# sourced script to login
source("code/login_movebank_rizzolo.R", local = knitr::knit_global())
```

```{r load from Movebank, warning = FALSE}

# Get Movebank project info
FwsName <- "Spectacled_Eider_USFWS_Alaska"
studyIdFws <- getMovebankID(FwsName, login=Login)

# Download the Movebank location data into a data frame
locs_fws <- getMovebankLocationData(study=FwsName, sensorID="Argos Doppler Shift", login=Login, includeOutliers=TRUE)

### Download the associated Movebank reference data into a data frame
#ref_fws <- getMovebankReferenceTable(study=FwsName,login=Login)
```
### Filter data
Before plotting, remove: 

1. locations with missing sensor 1 (temperature) data, indicated with -999
2. records with special transmission data (every 4th duty cycle) that do not represent temperature, indicated by argos.sensor.3 = 0 
3. transmitters deployed before 2022

```{r filter data}
# Remove locations marked as outliers based on movement rates and directions using Douglas Argos Filter
#table(locs_fws$algorithm.marked.outlier)
locs_all <- locs_fws
#locs_filter <- subset(locs_fws, algorithm.marked.outlier != "true")
locs_start <- locs_all
#locs_start <- locs_filter

# remove NA data for transmitter sensor 1 (temperature) indicated with -999
locs <- subset(locs_start,  argos.sensor.1 != -999)

# remove special transmission (every 4th duty cycle) indicated by  argos.sensor.3 = 0 (see MTI Battery Powered PTT-100 Field Manual, p 17)
locs <- subset(locs,  argos.sensor.3 != 0)

#convert date field from factor to date format
locs$timestamp <- as.POSIXct(locs$timestamp, format = "%Y-%m-%d %H:%M:%S")

#convert sensor.01 values to deg C (from Microwave Telem field manual)
locs$btemp <- -28.682 + 0.3609*locs$argos.sensor.1

# look at distribution of btemp
#hist(locs$btemp)

# create list of active transmitters with timestamp year > 2021 (i.e., remove transmitters from the 2018 deployment)
active <- subset(locs, format(locs$timestamp, format("%Y")) > 2021)
#hist(active$btemp)
```

### Plot transmitter temperature by transmitter ID

Mortalities will be indicated by temperatures consistently below 40 째C (the range of temperatures likely associated living eiders is indicated by the green band in the plots). Departures from 40 째C unrelated to mortality happen. Mortalities will be indicated by multiple temperature readings < 40 째C. Adult transmitters (with transmitter IDs starting with 197) are programmed to transmit every 6.6 days until early December 2022 and then will increase to every 2 days until mid-April 2023. Juvenile transmitters (with transmitter IDs starting with 229) transmit every 2 days. Transmitters may miss duty cycles and some have not transmitted for prolonged periods without any indication of mortality. 

```{r plots, warning = FALSE, message = FALSE}
for(var in unique(active$tag.local.identifier)){
  print(ggplot(active[active$tag.local.identifier==var,], aes(timestamp, btemp))+
          geom_rect(ymin = 38,ymax = 42,xmin = -Inf,xmax = Inf,fill = "green")+
          geom_point()+
          geom_line()+
          ylim(min(active$btemp), max(active$btemp))+
          scale_x_datetime(limits = c(min(active$timestamp), max(active$timestamp)))+
          geom_vline(xintercept = yesterday, color = "blue", linetype = 4) +
          ggtitle(label = var)
  )
}
```
